---
title: "My Cluster Setup and Some XML"
author: "John Muschelli"
date: "November 12, 2014"
output: ioslides_presentation
---

## Step 1: SSH Keys

- Ask Jiong for a Login

Passwordless Logins:

- <http://www.biostat.jhsph.edu/bit/nopassword.html>
- <http://www.linuxproblem.org/art_9.html>
- How does it work?

## Step 1: SSH Keys

- Make key on your machine `ssh--keygen -t rsa`
- DSA or RSA? See [Check out StackOverflow](http://security.stackexchange.com/questions/5096/rsa-vs-dsa-for-ssh-authentication-keys)
- Key is in a `.pub` file
<img src = "key.jpg", style="width:500px;  display: block; margin: auto;">

## Step 2: Send to the Cluster

- Use [Cyberduck](https://cyberduck.io/?l=en) (Mac) or [WinSCP](http://winscp.net/eng/index.php) (Windows) or `rsync` (in Terminal) to send to cluster
- Go on cluster, copy to `.ssh` folder.
- `cat file.pub >> authorized_keys`, (`>>` means append)
- Do the SAME thing on the cluster, creating `jhpce_file.pub`, and then do
`cat jhpce_file.pub >> authorized_keys`
  - This will allow for passwordless **node** login

## Step 3: Login into node from one command

- Typing Passwords is BORING and inefficient
- Check out Leo's post for `qr`: <http://lcolladotor.github.io/2013/12/11/quick-cluster-login-to-interactive-session/>
c
In `.bash_profile` (defining environment variables and aliases):
```{r, engine='bash'}
jhpce_num="02"
jenig="jmuschel@jhpce${jhpce_num}.jhsph.edu"
jdenig="jmuschel@jhpce03.jhsph.edu"
alias justenigma="ssh -Y -X $jenig"
```


## My addition: `qrgig`

Use `qrgig 5 6`:
```{r, engine='bash'}
qrgig(){
    x="$1"
    y="$2"
    y="${y}G"
    x="${x}G"
    # echo "${x}"
    # echo "${y}"
    ell="-l mem_free=$x,h_vmem=$y,$3"
    echo "qrsh requests were: $ell"
    cmd="source /etc/profile; echo \"cd \$PWD\" > ~/.bash_pwd; history -w; qrsh $ell"
    # echo "$cmd"
    justenigma -t $cmd
}
```

## Text Editor

- I recommend Sublime Text 2 (Cross-platform, but not free)
- Atom.io is good, similar to Sublime.
- Textmate is also good
- All can use `rmate` (ssh forwarding)
- <https://atom.io/packages/remote-atom>


## Port Forwarding

This link allows you to forward your code to a local machine: 
<http://erniemiller.org/2011/12/12/textmate-2-rmate-awesome/>

Then put this in  your `.bash_profile` on the cluster, changing `MYPORT` to a unique number:
`alias subl="rmate -p MYPORT"`

Then put this in your local `.bash_profile`:

`alias enigma="ssh -Y -X -R MYPORT:localhost:52698 ${jenig}"`

Go onto JHPCE, then type `subl FILE`

(Demo)


## Other options

- Use Git and use a lot of push/pulls to maintain cluster
- I usually use git, with remote repo (GitHub), then `rsync` to cluster
- Make aliases to places syncing regularly
  - `syncprog` demo.


## XML package

- XML - Extensible Markup Language (XML)  - like LaTeX/HTML, but usually for documents/data
- Use for parsing XML and HTML tables
- Use XPath - query language

## Other efficiencies

- Make aliases for commonly navigated paths
- Make a `qcwd` alias
- Make an `Rbatch` alias


## (My) Mostly used commands

- `xmlParse`/`htmlParse`
- `readHTMLTable`
- `readHTMLList`
- `xmlValue`
- `xmlChildren`
- `xmlAttrs`
- `getNodeSet` 
- `xpathApply`/`xpathSApply`

## CDC Example

[Check out my Blog Post about XML example](http://hopstat.wordpress.com/2014/01/14/faster-xml-conversion-to-data-frames/)

<http://www.cdc.gov/vaccines/programs/vfc/awardees/vaccine-management/price-list/archive.html>

<http://www.cdc.gov//vaccines/programs/vfc/awardees/vaccine-management/price-list/2012/2012-02-01.html>

